%% 摘要

\begin{abstractzh}

\noindent{\heiti\zihao{-4} 摘要：}

随着大语言模型的快速发展，人工智能应用正从单一的问答交互向具备自主规划、工具调用和流程执行能力的智能体演进。在企业级业务场景中，构建 Agent 应用不仅需要降低开发门槛，更要求执行过程高度可观察、关键结果可校验以及异常操作可追溯。目前，业界已涌现出部分低代码编排平台与 Agent 开发框架，能够有效支持基础工作流的搭建与自动化执行。然而，现有方案在实际业务落地中仍面临两项突出痛点：一方面，在主流的 Java 业务系统中，成熟的 Agent 可视化编排实践相对匮乏；另一方面，现有工作流引擎多采用“一跑到底”的黑盒执行模式，缺乏在关键节点暂停、由人工介入审核、动态修改中间结果并恢复执行的机制，难以满足高风险业务流对“自动执行 + 人工把关的安全合规要求。

针对上述需求痛点，本文设计并实现了一套基于 Spring Boot 的 AI Agent 可视化编排与可控执行系统。系统采用前后端分离与分层架构设计，前端基于 React 与 React Flow 构建可视化 DAG 流程画布；后端依循接口层、应用层、领域层和基础设施层组织核心逻辑。系统核心涵盖 Agent 配置管理、工作流调度引擎、人工审核介入机制、知识检索增强及安全认证模块。在关键技术实现上，系统通过版本快照保障配置追溯，基于 DAG 调度推进节点状态，并利用 SSE 机制实现前端运行轨迹的实时推送。为彻底解决关键节点缺乏人工把关的问题，系统在执行引擎中引入了“执行前”与“执行后”两类人工检查点机制——流程到达检查点后自动挂起并入队，审核人员可全盘查看上下文、干预并修正中间结果后决定放行或终止。底层进一步结合 Redis 队列、分布式锁、乐观锁及审批持久化等技术，确保了并发审批状态的强一致性与过程可溯源性。

系统运行测试结果表明，本文平台完整打通了从 Agent 建模创建、可视化发布、自动化执行到人工干预控制的核心功能闭环，切实满足了业务系统对 AI 工作流可控性的要求，对在 Java 生态下构建安全、可靠的智能体执行平台具有良好的工程实践价值。

\keywordszh{AI Agent；智能体编排；Spring Boot；工作流编排；人工审核检查点}

\end{abstractzh}

\begin{abstracten}

\noindent{\bfseries\zihao{-4} Abstract: }The development of large language models is driving artificial intelligence applications from question-answering interaction toward AI Agents capable of task planning, tool invocation and workflow execution. In enterprise scenarios, agent applications need not only low development barriers, but also observable execution, verifiable key results and traceable operations. Existing low-code orchestration platforms and agent development frameworks can support workflow construction and automated execution, but visual orchestration practices in Java-based business systems are still relatively limited. In addition, many workflows run continuously from start to finish once triggered, lacking mechanisms to pause at key nodes, conduct human review, modify intermediate results and resume execution. This makes it difficult to meet the requirements of high-risk business processes that combine automation with human control.

To address these issues, this thesis designs and implements an AI Agent orchestration system based on Spring Boot. The system targets application builders and business users, aiming to provide integrated capabilities for visual modeling, controllable execution, human review and execution tracking. It adopts a separated front-end/back-end architecture and a layered back-end design, organizing business logic into the interface, application, domain and infrastructure layers. The front end is built with React, TypeScript and React Flow to provide a visual workflow canvas. The core modules include agent management, workflow scheduling and execution, human review with workflow resumption, knowledge-base retrieval enhancement, and user authentication with security support.

In implementation, the system stores agent configurations through version snapshots, advances workflow node states through DAG scheduling, and pushes real-time execution progress to the front end through SSE. To address the lack of human control at key nodes, the workflow engine introduces two types of human checkpoints: before node execution and after node execution. When a workflow reaches a checkpoint, execution is paused and a pending review task is created. Reviewers can inspect the context, approve the workflow with modified intermediate results, or reject and terminate the workflow. A Redis-based queue, distributed locks, optimistic locking and persistent review records are used to ensure state consistency and process traceability under concurrent review scenarios. The system also supports knowledge enhancement and secure access through asynchronous document processing, Milvus vector retrieval and user authentication. The running results show that the system implements the core functional closed loop from agent creation, workflow publishing and automated execution to human review and workflow resumption, demonstrating practical engineering value for building controllable and traceable agent execution platforms in Java-based business systems.

\keywordsen{AI Agent; Agent Orchestration; Spring Boot; Workflow Orchestration; Human-in-the-loop}

\end{abstracten}

\clearpage
